Refunctionalization of Abstract Abstract Machines (Functional Pearl)

### 2018-03-17 paper.tex
Proofreading related work

\textbf{Abstracting Abstract Machines.}

\textbf{Defunctionalization and Refunctionalization.}

Defunctionalization and refunctionalization build connections between abstract
machines and interpreters.

>>>>

\textbf{Abstract Interpretation and Control-flow Analysis.}
\citeauthor{cousot1977abstract} invented abstract interpretation as a sound approach
to approximate a program's runtime behavior\cite{cousot1977abstract}.
Control flow analysis is one instance of abstract interpretation on functional programs
that can be traced to Jones \cite{jones1981flow}.
\citeauthor{Shivers:1988:CFA:53990.54007} introduces $k$-CFA which uses $k$ recent calling contexts as program contour that differentiates values from different contexts \cite{Shivers:1988:CFA:53990.54007, Shivers:1991:SSC:115865.115884}.
The modern formulation of control flow analysis is the abstracting abstract machines
methodology \cite{van2012systematic, van2010abstracting} which forms the starting point of this paper.
Modern programming languages such as Java\cite{might2010resolving} and Racket \cite{Tobin-Hochstadt:2012:HSE:2384616.2384655}
can also be modeled by the abstracting abstract machine approach.

\textbf{Defunctionalization and Refunctionalization.}
Defunctionalization and refunctionalization build connections between abstract
machines and interpreters.
